Portfolio prioritization of salmon conservation

### 2013-04-10 inst/examples/salmonport.Rmd
modificiations right before 2013-04-10 meeting

*Other title ideas:*  
- Portfolio optimization reveals...  
- something more general with animals instead of just salmon?  
- Portfolio theory reveals conservation strategies that...  
- Intelligent tinkering with ecological portfolios: patterns of environmental response diversity drive salmon conservation priorities  
- Keeping every cog and wheel...

@@

```{r env-ts, fig.height=4, fig.width=4, cache = FALSE, fig.cap="Example temperature time series\\label{fig:env-ts}"}
#library(metafolio)
#or for rapid development:
library(devtools)
load_all("../../") # assuming you're 2 folders deeper than the package
source("plot_env_ts.R")
col_pal <- rev(gg_color_hue(10))
```

@@

```{r plot-cons-plans-curves, cache=FALSE, fig.width=3.3, fig.height=5.0, fig.cap="Different ways of prioritizing conservation. The curves show the environmental-tolerance curves for the populations that are conserved. The colours are the same as earlier and identify the different populations. These are in the same order as they are referred to in the next two plots: full range of environmental response diversity, most stable only, one half, other half, most asynchronous.", cache=FALSE}
#Notes #
#-b is "unfished equilibrium stock size"
source("plot_thermal_curves_scenarios.R")
```

```{r plot-cons-plans-mv, fig.width=6.5, fig.height=3.5, fig.cap="Conservation plans in mean-variance space. The dots show portfolios from individual simulation runs. The dark and light shaded areas show 25% and 75% quartiles. The left panel shows a scenario with a stationary environmental signal and strong short-term environmental noise. The right panel shows a scenario with a linearly-increasing environmental signal and minimal short-term environmental noise. These two scenarios bound the two environmental extremes: strong short-term noise with minimal long-term signal vs. a strong long-term signal with minimal short-term signal. Notice what happens to the two *half* conservation strategies. A more realistic scenario combines the two kinds of environmental noise. The efficient frontier is shown for the displayed portfolios. This isn't necessarily the overall efficient frontier.", cache=FALSE}
#Notes #
#-b is "unfished equilibrium stock size"
require(RColorBrewer)
cols <- brewer.pal(5, "Dark2")[c(1,2,4,5,3)] 
source("cons_plans.R")
```

@@

>>>>

*Other title ideas:*  
- Portfolio optimization reveals...  
- something more general with animals instead of just salmon?  
- Portfolio theory reveals conservation strategies that...  
- Intelligent tinkering with ecological portfolios: patterns of environmental response diversity drive salmon conservation priorities  
- Keeping every cog and wheel...  
- A yin for every yang...

@@

```{r env-ts, fig.height=4, fig.width=4, cache = FALSE, fig.cap="Example temperature time series\\label{fig:env-ts}"}
#library(metafolio)
#or for rapid development:
library(devtools)
metafolio_files <-  list.files(path = "../../R/")
for(i in 1:length(metafolio_files)){
   source(paste("../..//R/", metafolio_files[i], sep = ""));rm(i)}
#load_all("../../") # Not working with knitr?
source("plot_env_ts.R")
col_pal <- rev(gg_color_hue(10))
```

@@

```{r plot-cons-plans-curves, cache=FALSE, fig.width=3.3, fig.height=5.0, fig.cap="Different ways of prioritizing conservation. The curves show the environmental-tolerance curves for the populations that are conserved. The colours are the same as earlier and identify the different populations. These are in the same order as they are referred to in the next two plots: full range of environmental response diversity, most stable only, one half, other half, most asynchronous."}
#Notes #
#-b is "unfished equilibrium stock size"
col_pal <- rev(gg_color_hue(10))
source("plot_thermal_curves_scenarios.R")
```

\begin{figure}[htbp]
  \centering
    \includegraphics[height=5.0in]{thermal-curve-scenarios.pdf}
 \caption{Different ways of prioritizing conservation. The curves show the environmental-tolerance curves for the populations that are conserved. The colours are the same as earlier and identify the different populations. These are in the same order as they are referred to in the next two plots: full range of environmental response diversity, most stable only, one half, other half, most asynchronous.}
  \label{fig:sim-diagram}
\end{figure}

```{r plot-cons-plans-mv, fig.width=6.2, fig.height=3.3, fig.cap="Conservation plans in mean-variance space. The dots show portfolios from individual simulation runs. The dark and light shaded areas show 25% and 75% quartiles. The left panel shows a scenario with a stationary environmental signal and strong short-term environmental noise. The right panel shows a scenario with a linearly-increasing environmental signal and minimal short-term environmental noise. These two scenarios bound the two environmental extremes: strong short-term noise with minimal long-term signal vs. a strong long-term signal with minimal short-term signal. Notice what happens to the two *half* conservation strategies. A more realistic scenario combines the two kinds of environmental noise. The efficient frontier is shown for the displayed portfolios. This isn't necessarily the overall efficient frontier.\\label{fig:cons-plans-mv}", cache=FALSE}
#Notes #
#-b is "unfished equilibrium stock size"
require(RColorBrewer)
cols <- brewer.pal(5, "Dark2")[c(1,2,4,5,3)] 
source("cons_plans.R")
```

@@

```{r plot-cons-plans-n-mv, fig.width=6.2, fig.height=3.3, fig.cap="Conservation plans in mean-variance space. **This version shows conservation plans with balanced response diversity but different numbers of populations.** Notice how the left panel (strong short-term environmental variability) and the right panel (strong long-term environmental shift) look approximately the same. This illustrates (in this contrived example) how the number of populations decreases metapopulation variance through statistical averaging of non-systematic sources of stochasticity. The perfectly balanced environmental tolerances counteract the environmental fluctuations. In the real world, you wouldn't know the exact environmental tolerances, and so conserving more populations might increase your chances of retaining populations with a diversity of environmental tolerances. The orange blob in this figure matches the ``Full range of responses'' blob in Fig.\\ \\ref{fig:cons-plans-mv}. The dots show portfolios from individual simulation runs. The dark and light shaded areas show 25% and 75% quartiles.", cache=FALSE}
source("cons_plans_n.R")
```

### 2013-04-10 inst/examples/salmonport.tex
modificiations right before 2013-04-10 meeting

\emph{Other title ideas:}\\- Portfolio optimization reveals\ldots{}\\-
something more general with animals instead of just salmon?\\- Portfolio
theory reveals conservation strategies that\ldots{}\\- Intelligent
tinkering with ecological portfolios: patterns of environmental response
diversity drive salmon conservation priorities\\- Keeping every cog and
wheel\ldots{}

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure/plot-cons-plans-curves.pdf}
\caption{Different ways of prioritizing conservation. The curves show
the environmental-tolerance curves for the populations that are
conserved. The colours are the same as earlier and identify the
different populations. These are in the same order as they are referred
to in the next two plots: full range of environmental response
diversity, most stable only, one half, other half, most asynchronous.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{figure/plot-cons-plans-mv.pdf}
\caption{Conservation plans in mean-variance space. The dots show
portfolios from individual simulation runs. The dark and light shaded
areas show 25\% and 75\% quartiles. The left panel shows a scenario with
a stationary environmental signal and strong short-term environmental
noise. The right panel shows a scenario with a linearly-increasing
environmental signal and minimal short-term environmental noise. These
two scenarios bound the two environmental extremes: strong short-term
noise with minimal long-term signal vs.~a strong long-term signal with
minimal short-term signal. Notice what happens to the two \emph{half}
conservation strategies. A more realistic scenario combines the two
kinds of environmental noise. The efficient frontier is shown for the
displayed portfolios. This isn't necessarily the overall efficient
frontier.}
\end{figure}

@@

>>>>

\emph{Other title ideas:}\\- Portfolio optimization reveals\ldots{}\\-
something more general with animals instead of just salmon?\\- Portfolio
theory reveals conservation strategies that\ldots{}\\- Intelligent
tinkering with ecological portfolios: patterns of environmental response
diversity drive salmon conservation priorities\\- Keeping every cog and
wheel\ldots{}\\- A yin for every yang\ldots{}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[height=5.0in]{thermal-curve-scenarios.pdf}
 \caption{Different ways of prioritizing conservation. The curves show the environmental-tolerance curves for the populations that are conserved. The colours are the same as earlier and identify the different populations. These are in the same order as they are referred to in the next two plots: full range of environmental response diversity, most stable only, one half, other half, most asynchronous.}
  \label{fig:sim-diagram}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{figure/plot-cons-plans-mv.pdf}
\caption{Conservation plans in mean-variance space. The dots show
portfolios from individual simulation runs. The dark and light shaded
areas show 25\% and 75\% quartiles. The left panel shows a scenario with
a stationary environmental signal and strong short-term environmental
noise. The right panel shows a scenario with a linearly-increasing
environmental signal and minimal short-term environmental noise. These
two scenarios bound the two environmental extremes: strong short-term
noise with minimal long-term signal vs.~a strong long-term signal with
minimal short-term signal. Notice what happens to the two \emph{half}
conservation strategies. A more realistic scenario combines the two
kinds of environmental noise. The efficient frontier is shown for the
displayed portfolios. This isn't necessarily the overall efficient
frontier.\label{fig:cons-plans-mv}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure/plot-cons-plans-n-mv.pdf}
\caption{Conservation plans in mean-variance space. \textbf{This version
shows conservation plans with balanced response diversity but different
numbers of populations.} Notice how the left panel (strong short-term
environmental variability) and the right panel (strong long-term
environmental shift) look approximately the same. This illustrates (in
this contrived example) how the number of populations decreases
metapopulation variance through statistical averaging of non-systematic
sources of stochasticity. The perfectly balanced environmental
tolerances counteract the environmental fluctuations. In the real world,
you wouldn't know the exact environmental tolerances, and so conserving
more populations might increase your chances of retaining populations
with a diversity of environmental tolerances. The orange blob in this
figure matches the ``Full range of responses'' blob in
Fig.~\ref{fig:cons-plans-mv}. The dots show portfolios from individual
simulation runs. The dark and light shaded areas show 25\% and 75\%
quartiles.}
\end{figure}
